draft

### 2025-05-20 draft.tex
Add Alan as correspondig author
remove paragraph out of place
improve first results paragraph

% Created 2025-05-20 Tue 11:40
% Intended LaTeX compiler: pdflatex
\documentclass{article}

@@

\icmlcorrespondingauthor{Shantanu Singh}{shantanu@broadinstitute.org}

@@

The intended audience for such a featurization tool would be, in addition to biologists, data scientists striving to achieve reproducible data analyses within a few lines of code. As a whole, engineered features still have the role of, at the minimum, complementing deep learning ones. The bioimage software ecosystems lacks a modular tool to convert images into interpretable features with no compulsory graphical interfaces or cloud compute. Ideally it should also harmonize with other scientific libraries. With all this in mind we have developed cp\_measure.
\section{Extracting interpretable features}
\label{sec:org61842b5}
We build cp\_measure by extracting the CellProfiler measurements from the code base and grouping them based on their inputs: One object and one imaging channel (e.g., intensity, texture), one object and multiple channels (e.g., Pearson correlation) and multiple objects (e.g., number of neighbours).

@@

Our aim is to remain consistent with the current scientific Python ecosystem. Its interface corresponds that of the widely used scikit-image. This greatly reduces the effort needed to integrate it in existing workflows and tools.

>>>>

% Created 2025-05-20 Tue 13:14
% Intended LaTeX compiler: pdflatex
\documentclass{article}

@@

\icmlcorrespondingauthor{Al\'an F. Mu\~{n}oz}{amunozgo@broadinstitute.org}
\icmlcorrespondingauthor{Shantanu Singh}{shantanu@broadinstitute.org}

@@

The intended audience for such a featurization tool would be, in addition to biologists, data scientists striving to achieve reproducible data analyses within a few lines of code. As a whole, engineered features still have the role of, at the minimum, complementing deep learning ones. The bioimage software ecosystems lacks a modular tool to convert images into interpretable features with no compulsory graphical interfaces or cloud compute. Ideally it should also harmonize with other scientific libraries. With all this in mind we have developed cp\_measure.
\section{Extracting interpretable features}
\label{sec:org61842b5}
In our library cp\_measure we extracted the CellProfiler measurements, removed anything that is not essential to solve the image-to-features problem and categorized the measurenents based on their input: One object and one imaging channel (e.g., intensity, texture), one object and multiple channels (e.g., Pearson correlation) and multiple objects (e.g., number of neighbours).

@@
